Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-08-30 paper/paper.tex
added preliminary datacube plot
updated the timings benchmarks with more datacubes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{./figures/timing.eps}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./figures/demo-rectified-cube.png}
    \caption{Georectified Hyperspectral Datacube}
    \label{fig:rectified-cube}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{./figures/regrid-timing.eps}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig-regridding-timing}}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=10.5 cm]{./figures/reflectance-timing.eps}
  \caption{Description \label{fig-reflectance-timing}}
\end{figure}

@@

\begin{table}[H]
  \caption{Loading and Reflectance Conversion Times.\label{tab1}}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\textwidth}{CC}
    \toprule
    \textbf{Number of scan lines}	& \textbf{Execution time (s)}\\
    \midrule
    371		&   2.049	\\
    725    &   4.219	\\
    1000     &   5.875   \\
    \bottomrule
  \end{tabularx}
\end{table}
